Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-12 mtjournal.tex
whitespace and formatting cleanups [small acknowledgments]
incorporated Mari's suggested sentence on tuning

These challenges have motivated a search for better measures that
incorporate additional language knowledge sources.  METEOR
\cite{banerjee05meteor}, for example, uses synonym tables and
morphological stemming to do progressively more-forgiving matching.
It can be tuned towards recall or precision, but is generally not
tuned by users.  TERp \cite{snover09terp} is an extension of the
previously-mentioned TER that also incorporates synonym sets, along
with automatically-derived paraphrase tables.  TERp is explicitly
intended to be tuned to a development set by users.

TO DO: DISCUSS TUNING'S VIRTUES, FLAWS

@@

The GALE 2.5 translation corpus is made up of system translations into
English from three sites.
% MO added:
The three sites all use system combination to integrate results from
multiple systems, some of which are phrase-based and some which may
use syntax on either the source or target side. No system provided
system-generated parses.
%
The corpus being translated comes from
Arabic and Chinese in four genres: \texttt{bc} (broadcast
conversation), \texttt{bn} (broadcast news), \texttt{nw} (newswire),
and \texttt{wb} (web text), with corpus sizes shown in
table~\ref{tab:galestats}.
\begin{table}
  \begin{tabular}{r|rr|rr|rr}
    \hline
     & \multicolumn{2}{c|}{Arabic} & \multicolumn{2}{c|}{Chinese}
     & \multicolumn{2}{c}{Total}\\
     & doc & sent & doc & sent & doc   & sent\\
     \hline
     \texttt{bc}    & 59  & 750 & 56 & 1061 & 115 & 1811\\
     \texttt{bn}    & 63  & 666 & 63 & 620  & 126 & 1286\\
     \texttt{nw}    & 68  & 494 & 70 & 440  & 138 & 934 \\
     \texttt{wb}    & 69  & 683 & 68 & 588  & 137 & 1271\\
     \hline
     Total & 259 & 2593& 257& 2709 & 516 & 5302\\
     \hline
  \end{tabular}
  \caption{Corpus statistics for the GALE 2.5 translation
    corpus.}
  \label{tab:galestats}
\end{table}
The corpus includes one English reference translation $r_i$
\cite{gale08phase2_5references} for each sentence $i$ and a system
translation $t_{i,z}$ for each of the three systems $z$. Additionally,
each of the system translations of each segment $i$ has a
corresponding human-targeted reference aligned at the sentence level,
so we have available the HTER score of each segment
HTER$(t_{i,z})$ at both the sentence and document level.

@@

TO DO: NOTE RE: DELTAS

@@

% \appendix

% [don't think we want an appendix]

@@

This material is based upon work supported by the National Science
Foundation under Grant No. 0741585 and the Defense Advanced Research
Projects Agency under Contract Nos. HR0011-06-C-0022 and HR0011-06-C-0023.

@@

Any opinions, findings, and conclusions or recommendations expressed
in this material are those of the author(s) and do not necessarily
reflect the views of the National Science Foundation or the Defense
Advanced Research Projects Agency.

>>>>

These challenges have motivated a search for better measures that
incorporate additional language knowledge sources.  METEOR
\cite{banerjee05meteor}, for example, uses synonym tables and
morphological stemming to do progressively more-forgiving matching.
It can be tuned towards recall or precision, but is generally not
tuned by users.  TERp \cite{snover09terp} is an extension of the
previously-mentioned TER that also incorporates synonym sets, along
with automatically-derived paraphrase tables.  TERp is explicitly
intended to be tuned to a development set by users.
%
Tuning has the advantage that the weight of different types of errors
can be adjusted to match the needs of the task, though it makes it
more difficult to compare results across tasks, particularly when
there is little data for tuning.

@@

The GALE 2.5 translation corpus is made up of system translations into
English from three sites.
%
The three sites all use system combination to integrate results from
multiple systems, some of which are phrase-based and some which may
use syntax on either the source or target side. No system provided
system-generated parses.
%
The corpus being translated comes from
Arabic and Chinese in four genres: \texttt{bc} (broadcast
conversation), \texttt{bn} (broadcast news), \texttt{nw} (newswire),
and \texttt{wb} (web text), with corpus sizes shown in
table~\ref{tab:galestats}.
\begin{table}
  \begin{tabular}{r|rr|rr|rr}
    \hline
     & \multicolumn{2}{c|}{Arabic} & \multicolumn{2}{c|}{Chinese}
     & \multicolumn{2}{c}{Total}\\
     & doc & sent & doc & sent & doc   & sent\\
     \hline
     \texttt{bc}    & 59  & 750 & 56 & 1061 & 115 & 1811\\
     \texttt{bn}    & 63  & 666 & 63 & 620  & 126 & 1286\\
     \texttt{nw}    & 68  & 494 & 70 & 440  & 138 & 934 \\
     \texttt{wb}    & 69  & 683 & 68 & 588  & 137 & 1271\\
     \hline
     Total & 259 & 2593& 257& 2709 & 516 & 5302\\
     \hline
  \end{tabular}
  \caption{Corpus statistics for the GALE 2.5 translation
    corpus.}
  \label{tab:galestats}
\end{table}
The corpus includes one English reference translation $r_i$
\cite{gale08phase2_5references} for each sentence $i$ and a system
translation $t_{i,z}$ for each of the three systems $z$. Additionally,
each of the system translations of each segment $i$ has a
corresponding human-targeted reference aligned at the sentence level,
so we have available the HTER score of each segment
HTER$(t_{i,z})$ at both the sentence and document level.

@@

@@

% \appendix
% [don't think we want an appendix]

@@

{\small
This material is based upon work supported by the National Science
Foundation under Grant No. 0741585 and the Defense Advanced Research
Projects Agency under Contract Nos. HR0011-06-C-0022 and HR0011-06-C-0023.

@@

Any opinions, findings, and conclusions or recommendations expressed
in this material are those of the author(s) and do not necessarily
reflect the views of the National Science Foundation or the Defense
Advanced Research Projects Agency.
}
